Dynamic Witnesses for Static Type Errors

### 2015-11-20 paper/pldi16-submission/interactive.tex
ugh, more graph apis

\paragraph{Update}
Figure~\ref{fig:traversing-graph} shows how we update the state
for each command.
%
The procedure @findExpr vs cmd e@ traverses the $\tr$
and the current visualization state to compute the new
expression that should be added to the visualization state
and @updState vs cmd e@ then updates the graph
by inserting the new expression appropriately, using one of
the following functions.
%
@putBefore vs e e'@ \hbox{(resp. @putAfter vs e e'@)}
returns the modified version of @vs@ where @e'@ is the
immediate predecessor of @e@ (resp. the immediate successor of @e@);
%
@putRoot vs e@ returns the modified version of @vs@ extended
with a new vertex @e@ that has no predecessor or successor, and,
%
@getRoot vs e@ returns the vertex (expression) obtained
by transitively following the predecessors of @e@ until a
source vertex.
%
@getSubterms vs e@ traverses the sub-term edges to decompose an
expression into a list of sub-expressions paired with their context.
%
@applyCtx vs e ctx@ applies @ctx@ to @e@, traversing the sub-term edges
in reverse to find the super-term of @e@.
%
@findApp vs e@ builds on top of @getSubterms@ to find the first
application sub-term (if any), \ie the first sub-term that looks like
$\eapp{v_1}{v_2}$.
%
@findValue vs e@ traverses the single-step edges to find the final value
that @e@ reduces to.
%
Note that the sub-term edges $\searrow$ allow us to decompose an
expression into a sub-expression and the surrounding context, thus
enabling the \stepintosym\ and \stepoversym\ traversals.

>>>>

\paragraph{Update}
Figure~\ref{fig:traversing-graph} shows how we update the state
for each command.
%
The procedure @findExpr vs cmd e@ traverses $\tr$
and the current visualization state to compute the new
expression that should be added to the visualization state
and @updState vs cmd e@ then updates the graph
by inserting the new expression appropriately, using one of
the following functions.
%
@putBefore vs e e'@ \hbox{(resp. @putAfter vs e e'@)}
returns the modified version of @vs@ where @e'@ is the
immediate predecessor of @e@ (resp. the immediate successor of @e@);
%
@putRoot vs e e'@ returns the modified version of @vs@ extended
with a new root vertex @e@ and its successor @e'@, and,
%
% @getRoot vs e@ returns the vertex (expression) obtained
% by transitively following the predecessors of @e@ until a
% source vertex.
%
@getNext vs e@ returns the immediate successor of @e@ in $\tr$.
%
@getPrev vs e@ computes the path @p@ between @e@ and its immediate
predecessor in the current visualization, and then returns @e@'s immediate
predecessor along @p@.
%
@getSubterms vs e@ traverses the sub-term edges to decompose an
expression into a list of sub-expressions paired with their context.
%
@applyCtx vs e ctx@ applies @ctx@ to @e@, traversing the sub-term edges
in reverse to find the super-term of @e@.
%
\hbox{@findApp vs e@} builds on top of @getSubterms@ to find the first
application sub-term (if any), \ie the first sub-term that looks like
$\eapp{v_1}{v_2}$.
%
@findVal vs e@ traverses the single-step edges to find the final value
that @e@ reduces to.
%
Note that the sub-term edges $\searrow$ allow us to decompose an
expression into a sub-expression and the surrounding context, thus
enabling the \stepintosym\ and \stepoversym\ traversals.
